Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
modif table timings

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/Octa_mean}}
    {\includegraphics[width=2.7cm]{figs/Octa_gaussian}}
    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{\emph{Third row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
  \emph{Second row:} First and second principal directions estimation (and zoom) on an OctaFlower.
  \emph{Third row:} Mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

@@

\begin{figure}[!htbp]
  \begin{center}
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymode = log,
          ymax = 6000,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar, color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000) 
          (Snow-R10,9.831000) (Snow-R20,9.653000)  (Dragon-R8,136.300000) (Dragon-R20,145.450000)};
        %l4
        \addplot+[ybar, color=black, fill=clquatre] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000) 
          (Snow-R10,6.085000) (Snow-R20,9.445000)  (Dragon-R8,3.389000) (Dragon-R20,20.228000)};
        %l3
        \addplot+[ybar, color=black, fill=cltrois] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
          (Snow-R10,10.629000) (Snow-R20,11.542000) (Dragon-R8,20.397000) (Dragon-R20,26.710000)};
        %l2
        \addplot+[ybar, color=black, fill=cldeux] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000) 
          (Snow-R10,13.777000) (Snow-R20,37.700000) (Dragon-R8,29.967000) (Dragon-R20,92.435000)};
        %l1
        \addplot+[ybar, color=black, fill=clun] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000) 
          (Snow-R10,39.627000) (Snow-R20,217.954000) (Dragon-R8,59.840000) (Dragon-R20,506.549000)};
        %l0
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000) 
          (Snow-R10,236.194000) (Snow-R20,1655.680000) (Dragon-R8,322.674000) (Dragon-R20,3763.422000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
	  \end{tikzpicture}
%
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymax = 6000,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          %ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20, 
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar,color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000) 
          (Snow-R10,9.383000) (Snow-R20,9.767000)  (Dragon-R8,127.347000) (Dragon-R20,127.166000)};
        %Hierarchical measurement
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000) 
          (Snow-R10,96.747000) (Snow-R20,364.547000)  (Dragon-R8,147.662000) (Dragon-R20,787.459000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
     \end{tikzpicture}
     \end{center}
  %
  \caption{Timings in milliseconds obtained while visualizing an adaptive
  triangulation on three objects -- OctaFlower (digital domain of $130^3$ ), Snow
  Microstructures ($233^3$) and XYZ-Dragon ($510^3$) --  by computing the
  curvature with a regular grid (\emph{left}) and with hierarchical
  algorithm (\emph{right}), with two different radii for each object.
  %
  In \emph{orange color}: time required to extract the triangulation.
  %
  In \emph{blue color}: time required to compute the curvature tensor at
  different levels: from $l_4$ (light blue) to $l_0$ (dark blue).
  %
  }
  %
  \label{fig:timings}
\end{figure}

In this experiments, we measure the timings obtained when running our framework on a
GeForce GTX 850M. Here, the triangulation is dynamically refining according to its distance to the camera.
At each frame, both the curvature and the triangulation are recomputed.
If the visualisation stays unchanged, we compute the curvature at a level $l-1$ until the level $l_0$ is reached.
We measured those timings using the regular and the hierarchical algorithm. The results are presented in 
logarithmic scale figure \ref{fig:timings}.

@@

%\subsection{Visualisation}
%
%For dynamic datasets, we consider a time varying implicit
%surface. Since it would have been to expensive to update the a mipmap texture
%of densities at each time step, we simply evaluate the implicit
%expression at each vertex of a cell to decide if such cell is included
%or not into $\Ball{R}{\vx}\cap \Shape$.
%\todo[inline]{blabla experiments}

@@

In this article, we have propose a full data parallel framework on GPU
hardware which combines an adaptive isosurface construction from
digital data with a curvature tensor estimation at each vertex. Using
this approach, we can explore in realtime different curvature
measurements (mean, Gaussian, principal directions) with different
ball radii on potentially large dynamic dataset. Our proposal relies
on both a linear octree representation with Morton codes and an
efficient integral computation on GPU.  The source code and additional
material (video, \ldots) are available on the project website
(\url{https://github.com/dcoeurjo/ICTV}).

>>>>

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/Octa_mean}}
    {\includegraphics[width=2.7cm]{figs/Octa_gaussian}}
    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{\emph{First row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
  \emph{Second row:} First and second principal directions estimation (and zoom) on an OctaFlower.
  \emph{Third row:} Mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

@@

\begin{figure}[!htbp]
  \begin{center}
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymode = log,
          ymax = 6000,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar, color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000)
          (Snow-R10,9.831000) (Snow-R20,9.653000)  (Dragon-R8,136.300000) (Dragon-R20,145.450000)};
        %l4
        \addplot+[ybar, color=black, fill=clquatre] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000)
          (Snow-R10,6.085000) (Snow-R20,9.445000)  (Dragon-R8,3.389000) (Dragon-R20,20.228000)};
        %l3
        \addplot+[ybar, color=black, fill=cltrois] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
          (Snow-R10,10.629000) (Snow-R20,11.542000) (Dragon-R8,20.397000) (Dragon-R20,26.710000)};
        %l2
        \addplot+[ybar, color=black, fill=cldeux] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000)
          (Snow-R10,13.777000) (Snow-R20,37.700000) (Dragon-R8,29.967000) (Dragon-R20,92.435000)};
        %l1
        \addplot+[ybar, color=black, fill=clun] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000)
          (Snow-R10,39.627000) (Snow-R20,217.954000) (Dragon-R8,59.840000) (Dragon-R20,506.549000)};
        %l0
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000)
          (Snow-R10,236.194000) (Snow-R20,1655.680000) (Dragon-R8,322.674000) (Dragon-R20,3763.422000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
	  \end{tikzpicture}
%
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymax = 6000,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          %ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar,color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000)
          (Snow-R10,9.383000) (Snow-R20,9.767000)  (Dragon-R8,127.347000) (Dragon-R20,127.166000)};
        %Hierarchical measurement
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000)
          (Snow-R10,96.747000) (Snow-R20,364.547000)  (Dragon-R8,147.662000) (Dragon-R20,787.459000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
     \end{tikzpicture}
     \end{center}
  %
  \caption{Timings in milliseconds (in logscale) obtained while visualizing an adaptive
  triangulation on three objects -- OctaFlower (digital domain of $130^3$ ), Snow
  Microstructures ($233^3$) and XYZ-Dragon ($510^3$) --  by computing the
  curvature with a regular grid (\emph{left}) and with hierarchical
  algorithm (\emph{right}), with two different radii for each object.
  %
  In \emph{orange color}: time required to extract the triangulation.
  %
  In \emph{blue color}: time required to compute the curvature tensor at
  different levels: from $l_4$ (light blue) to $l_0$ (dark blue).
  %
  Timings are given using a NVIDIA GeForce GTX 850M GPU.
  }
  %
  \label{fig:timings}
\end{figure}

When dealing with large datasets, we can not expect real-time curvature tensor
estimation due to the huge amount of data to process. By computing an
dynamically refined approximate curvature tensor estimation joined with an
adaptive triangulation (as discussed in Section~\ref{sec:hierarchical}), we
manage to maintain a real time framerate by giving control over the amount of
data to process at each frame. In Figure~\ref{fig:timings}, we compare timings
(in logarithmic scale) when the triangulation is dynamically refining according
to its distance to the camera. We measured those timings using the regular and
the hierarchical algorithm.

@@

\subsection{Visualisation}

For dynamic datasets, we consider a time varying implicit
surface. Since it would have been to expensive to update the a mipmap texture
of densities at each time step, we simply evaluate the implicit
expression at each vertex of a cell to decide if such cell is included
or not into $\Ball{R}{\vx}\cap \Shape$.
\todo[inline]{blabla experiments}

@@

In this article, we have propose a full data parallel framework on GPU
hardware which combines an adaptive isosurface construction from
digital data with a curvature tensor estimation at each vertex. Using
this approach, we can explore in real-time different curvature
measurements (mean, Gaussian, principal directions) with different
ball radii on potentially large dynamic dataset. Our proposal relies
on both a linear octree representation with Morton codes and an
efficient integral computation on GPU. The source code and additional
material (video, \ldots) are available on the project website
(\url{https://github.com/dcoeurjo/ICTV}).
